Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.

Now, we define the $\freorder_{∧}$ function in~\eqref{eq:reorder-and} to
reorder nested conjunctions. This will help us in the end of this section to
reorder conjunctive normal forms. For instance,

@@

In the last example in~\eqref{ex:reorder-example}, we could not build the conjunction
$r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal to $q ∨ p$.
We solve this issue in Lemma~\ref{lem:reorder-and-or} by
using the $\fconjunctor$ function defined in~\eqref{eq:conjunct-or}.
The purpose of this function consists of extracting a disjunction from
a conjunction, but without matter the order of inner disjunction.

@@

Now, we are ready to reconstruct the \resolve rule. This is the
first application of Lemma \ref{lem:reorder-and-or}.
The \resolve rule is a generalization of the resolution theorem.
This rule has three arguments: a positive literal $ℓ$ to apply the
resolution theorem and two derivations.

>>>>

Now, we define the $\freorder_{∧}$ function in~\eqref{eq:reorder-and} to
reorder nested conjunctions. This will help us in the end of this section to
reorder conjunctive normal forms.

@@

In the last example in~\eqref{ex:reorder-example}, we could not build the conjunction
$r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal to $q ∨ p$.
We solve this issue in Lemma~\ref{lem:reorder-and-or} by
using the $\fconjunctor$ function defined in~\eqref{eq:conjunct-or}.
The purpose of this function consists of extracting a disjunction from
a conjunction, but without matter the order of the inner disjunctions.

@@

Now, we are ready to reconstruct the \resolve rule using
Lemma~\ref{lem:reorder-and-or}.
The \resolve rule is a generalization of the resolution theorem.
This rule has three arguments: a positive literal $ℓ$ to apply the
resolution theorem and two derivations.
